% !TEX program = xelatex

\documentclass{resume}
%\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts
\usepackage{hyperref}
\usepackage{linespacing_fix}
\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Guangcan MAI}

% {E-mail}{mobilephone}{homepage}
% be careful of _ in emaill address
\contactInfo{csgcmai@life.hkbu.edu.hk}{+852 95656007}{\url{www.comp.hkbu.edu.hk/~csgcmai}}
% {E-mail}{mobilephone}
% keep the last empty braces!
%\contactInfo{xxx@yuanbin.me}{(+86) 131-221-87xxx}{}

\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{Hong Kong Baptist University (HKBU)}, Kowloon, Hong Kong SAR}{Sept. 2013 -- Present}
\textit{Ph.D student} in Computer Science (CS), expected in Nov. 2017
\datedsubsection{\textbf{Michigan State University}, East Lansing, US}{Feb. 2016 -- Aug. 2016}
\textit{Visiting Scholar}\ in \href{http://biometrics.cse.msu.edu/}{PRIP Lab}{, Dept. of Computer Science and Engineering}
\datedsubsection{\textbf{South China University of Technology (SCUT)}, Guangzhou, China}{2010 -- 2013}
\textit{B.Eng.} in Computer Science and Technology (CS)\\
\textit{* Selected by SCUT for a special program for most promising students and finished the program in 3 years}

\section{\faUsers\ Experience}
\datedsubsection{\textbf{Michigan State University} East Lansing, US}{Feb. 2016 -- Aug. 2016}
\role{Visiting Scholar}{\textit{Advisor}： \href{http://cse.msu.edu/~jain}{Prof. Anil K. Jain}}
- Research on facial image reconstruction from CNN representations
\datedsubsection{\textbf{Hong Kong Baptist University}\ Kowloon, Hong Kong SAR}{Sept. 2013 -- Present}
\role{Ph.D student}{Advisor： \href{http://www.comp.hkbu.edu.hk/~pcyuen}{Prof. Pong C. Yuen}}
- Research on multi-biometric (face, fingerprint and iris) template protection system, a binary feature fusion algorithm has been developed (details can be found in research paper) 
\datedsubsection{\textbf{South China University of Technology}\  Guangzhou, China}{May 2012 -- May 2013}
\role{Research undergraduate}{Advisor： Prof. Xingming Zhang}
- Develop a mobile surveillance system which base on Android, mobile camera and server\\
- Responsible for video stream extraction, transmission and Android client  \\
- A software copyright\\
- \textit{The First Prize} in International Contest of InnovAtioN (Guangdong) 
\datedsubsection{\textbf{South China University of Technology}\  Guangzhou, China}{May 2011 -- May 2012}
\role{Research undergraduate}{Advisor： Prof. Shaohua Tang and Dr. Xiaozheng Lai}
- Develop a low-cost encryption chip and control system using Xilinx FPGA\\
- Responsible for the development of control systems and sensors for data acquisition\\
- \textit{Third Prize} in OpenHW 2011\\
- \textit{The Most Favorite Project} in Guangdong First Colleague Innovation \& Startup Contest
%
\section{\faHeartO\ Awards and Honors}
\begin{itemize}
	\item \datedline{\textit{Four Year Ph.D Scholarship}，HKBU}{2013 -- 2017}
%	\item \datedline{\textit{Overseas Attachment Allowance}, Mr. Kwok Yat Wai and Madam Kwok Chung Bo Fun Graduate School Development Fund}{2016}
	\item \datedline{\textit{Third Prize}, ACM-ICPC (Hong Kong)}{Jun. 2014}
	\item \datedline{\textit{National Motivational Scholarship}}{2011, 2012}
	\item \datedline{\textit{Merit Student}，SCUT}{2011, 2012}
	\item \datedline{\textit{Nomination}, Top-ten Excellent Team in SCUT (20 teams are nominated)}{2012}
	\item \datedline{\textit{The Most Favorite Project}，Guangdong First Colleague Innovation}{Oct. 2012}
	\item \datedline{\textit{First Prize}， International Contest of InnovAtioN (Guangdong)}{Sept. 2012}
	\item \datedline{\textit{Third Prize}，Open Source Hardware and Embedding System Contest (20/218)}{Jun. 2012}
	\item \datedline{\textit{Second Prize}，Guangdong Robot Contest}{Sept. 2011}
	\item \datedline{\textit{Excellent Student Cadre}, SCUT}{2011}
\end{itemize}

\section{\faLink\ Services}
\datedsubsection{\textbf{Research Student Representative}\  Faculty of Science, HKBU}{2014 -- 2016}
\datedsubsection{\textbf{President}\  Chinese Students and Scholars Association (CSSA), HKBU}{2014 -- 2016}

\section{\faMicrophone \ Presentations}
\begin{itemize}
	\item\datedline{\textbf{Guangcan Mai}, \href{http://www.comp.hkbu.edu.hk/~csgcmai/papers/BinaryTemplateFusion_BTAS2015.pptx}{Fusing Binary Templates for Multi-biometric Cryptosystems}}{Sept. 2015}
	- Washington DC, US
\end{itemize}

\section{\faBook\ Publications}
\begin{itemize}
	\item \textbf{Guangcan Mai}, Meng-Hui Lim, Pong C Yuen, Fusing Binary Templates for Multi-biometric Cryptosystems. \textit{BTAS2015}
	\item \textbf{Guangcan Mai}, Meng-Hui Lim, Pong C Yuen, Binary Feature Fusion for Discriminative and Secure Multi-biometric Cryptosystems, invited submission, \textit{Image and Vision Computing} (under review)
	\item Meng-Hui Lim, Sunny Verma, \textbf{Guangcan Mai}, Pong C Yuen, Learning Discriminability-Preserving Histogram Representation from Unordered Features for Multibiometric Feature-Fused-Template Protection, \textit{Pattern Recognition}, Dec 2016, Pages 706–719
\end{itemize}


\section{\faCogs\ IT Skills}
% increase linespacing [parsep=0.5ex]
\begin{itemize}[parsep=0.5ex]
	\item Programming language: MATLAB, C/C++, Python, Java, PHP, VerlogHDL (ordered by proficiency)
	\item Platform and tools: Windwos, Linux, Android,  Vim, \LaTeX, Office, Git, Visual Studio, MXNET, FPGA
\end{itemize}

\section{\faInfo\ Others}
% increase linespacing [parsep=0.5ex]
\begin{itemize}[parsep=0.5ex]
	\item GitHub: \url{https://github.com/csgcmai}
	\item Language, Mandarin (Chinese), Cantonese, English
\end{itemize}
\end{document}
